\section{Introduction}
\subsection{Motivation}
The 21\textsuperscript{st} century is a time where one technology chases the other, everything new is the older version of tomorrow. Smartphones getting faster, smartwatches support the use of the phone. Virtual reality fascinates more and more people, even the TV is almost on a par with real persons in relation to communication and interaction.
One limiting thing of getting even smaller devices is the need of a possibility to interact with the device, such as keyboards or mouse cursors. Even with voice recognition getting better and better, keyboards are still an important tool to interact. Wether it is for fast programming or to write texts, the comfort of typing fast and an great amount of characters is very important.
One of the main reasons for our prototype is the fact that every keyboards needs its space. Even the small ones are often the limiting size of a device.  
The position of the keys is fixed in most of the cases. The user can remap the characters, but not the position of the key itself. Therefore the user can't personalize the keyboard which is bad in many cases.
For example persons who can't write the recommendet touch system (maybe because of deficient exercise or because of a lack of fingers).
There are many disadvantages of a keyboard, bot nonetheless typing is very effective and precise.
The goal is to make typing even more comfortable. Getting rid of the hardware and increasing the ergonomy of typing itself. Without the hardware and with own finger movements, typing will become an effective and fitting way to interact with machines.


% * tastaturen sind doof
%   - unhandlich
%   - geräte werden kleiner, aber nicht unbegrenzt wegen tastaturen
%   - sehnenscheidenentzündungen, erkrankung der unterarmmuskulatur (mikro risse) etc
%   - man muss immer an einem tisch sitzen, tippen im stehen ist einfach doof
%   - schwer anpassbar an körperliche fähigkeiten (vorgegebene, fixe anordnung)
%     * 10-Finger-tippen ist gar nicht so toll für Jedermann (Fingermangel, ...)
% * tippen ist cool
%   - wichtig ist präzise Eingabe von hunderten von zeichen (programmieren!)
%   - soll schnell sein
% * wir wollen tippen (zeicheneingabe) ohne tastatur, 
%   - flexibel
%   - keine große hardware

